\documentclass[12pt]{article}
\usepackage{lingmacros}
\usepackage{tree-dvips}
\usepackage{multicol}
\usepackage{titling}
\usepackage[a4paper, total={6in, 8in}, margin=0.5in, headheight=0.5in, tmargin=0.5in]{geometry}

\setlength{\droptitle}{0em}
\title{Carson Quigley}
\date{}


\begin{document}
\pagestyle{empty}

\begin{multicols}{3}

\begingroup
    \LARGE Carson Quigley\\[0em]
\endgroup

\vfill\null

\begin{itemize}
    \item[] (515)-505-9695
    \item[] linkedin.com/in/quigley-c

\vfill\null

    \item[] carson.ll.quigley@gmail.com
    \item[] Github: quigley-c

\vfill\null

\end{itemize}
\end{multicols}

\vspace{-1.5em}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\begingroup
\centering
\begin{multicols}{2}
\subsection*{Bachelors - Computer Science}
Allegheny College Class of 2020

\subsection*{Masters - Computer Science}
SUNY Binghamton Class of 2022

\end{multicols}
\endgroup

\begingroup
\centering
\section*{Objective}
I'm looking for a job to support myself while in school for a master's degree. 
Adaptive, empathetic, social, and proficient in many programming languages. 
In fact, this resume was written in LaTeX! Must be able to work around a school schedule.
\endgroup


\section*{Practical Experience}

\subsection*{Computer Science TA / Tutor}
Allegheny College Computer Science Department (Spring 2018 - Spring 2020)
Guiding students through programming concepts. Assisting the professor with teaching class.

\begin{multicols}{2}
\begin{itemize}
    \item Intro Java I
    \item Intro Java 2
    \item Intro Programming Mathematics
\end{itemize}
\end{multicols}

\subsection*{IT Internship}
U.S. Bankruptcy Court (Summer 2019)
Interning with professionals using skills in software development and time management. Shadowing and assisting members of the team, including the Systems Administrator.

\subsection*{Executive Board / Events and Electronics Manager}
Grounds For Change Coffee (Spring 2017 - Spring 2018)
Managing and training volunteers, Scheduling and setting up live music or other events that use the shop as a space.



\section*{Skills}

\begin{multicols}{2}
\begin{itemize}
    \item Programming Languages
    \item OOP Paradigms
    \item HTML / CSS
    \item \LaTeX
    \item Time Management
    \item Business Management
    \item Customer Service
\end{itemize}
\end{multicols}



\section*{Academic Achievments and Research}

\begin{multicols}{2}
\subsection*{Trustee Scholar}
Allegheny College (2016 - 2020)

\subsection*{Cupper Scholar}
Allegheny College (Summer 2018)

\subsection*{Mellon Fellow Research Grant}
Research Assistant - Professor Xiaoling Shi, Allegheny College (Summer 2017)

\subsection*{Cincala Fund for Research}
Research Assistant - Dr. Aravind Mohan, Allegheny College (Summer 2018)

\end{multicols}

\section*{Projects}

\subsection*{Undergraduate Thesis Work: Image Color Picking Tool}
The Image Color Picking Tool utilizes machine learning to quickly quantize color
in a user's background image and recommends a color scheme for the environment
based on the colors in the image.

\begin{multicols}{2}
\subsection*{GatorGrader}
\vfill\null

\subsection*{GatorGrouper}
\vfill\null

\end{multicols}

\end{document}
